decompr: GVC decomposition in R

### 2015-01-29 draft.Rnw
small layout fixes and cleanup in code
shifting tables, small layout fixes

\usepackage[latin1]{inputenc}
\usepackage{rotating}
\usepackage{adjustbox}
\usepackage{mathtools}
\usepackage{threeparttable}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{changepage}
\usepackage{lscape}
\usepackage{pbox}
\usepackage{array}
\usepackage[natbib, authordate, backend=biber]{biblatex-chicago}
\usepackage[hidelinks]{hyperref}

@@

\vspace{\stretch{1}}
\abstract{Global Value Chains have become a central unit of analysis in research on international trade. However, 
the complex matrix transformations at the basis of most Value Chain indicators still constitute a significant entry barrier
the field. The R package \textit{decompr} solves this problem by implementing algorithms for the analysis of Global Value Chains,
which calculate standard indicators in an automated fashion. Two methods for gross export flow decomposition using 
Inter-Country Input-Output tables are provided. The first method is the \textit{Wang-Wei-Zhu} algorithm which splits 
bilateral gross exports into 16 value added components. These components can broadly be divided into domestic and 
foreign value added in exports. The second method concerns a decomposition based on the classical \citet{wale36} insight.
It derives the value added origins of an industry's exports by source country and source industry, using easily available
gross trade data. This article summarises the methodology of the algorithms, describes the format of the input and output data, 
and exemplifies the usefulness of the two methods on the basis of a simple example data set.}
\pagebreak

@@

\begin{itemize}
 \item domestic value added in exports
 \item foreign value added in exports
 \item pure double counted terms
\end{itemize}

@@

  \caption{Leontief Decomposition}
  \label{tab:leon}
  \begin{tabular}{lccccccccc}
    \hline
          & Argentina. & Argentina. & Argentina. & Turkey. & Turkey. & Turkey. & Germany. & Germany. & Germany.\\
          & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport.\\
          & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
    \hline
    Argentina.Agriculture & 28.52 & 2.79  & 0.36  & 1.81  & 3.12  & 0.36  & 1.24  & 1.30  & 4.12 \\
    Argentina.Textile.and.Leather & 1.06  & 19.12 & 0.42  & 0.48  & 1.83  & 0.43  & 0.59  & 1.15  & 4.75 \\
    Argentina.Transport.Equipment & 0.21  & 0.14  & 1.06  & 0.03  & 0.08  & 0.04  & 0.02  & 0.07  & 0.19 \\
    Turkey.Agriculture & 0.72  & 1.34  & 0.12  & 34.93 & 7.00  & 1.48  & 2.55  & 1.52  & 6.18 \\
    Turkey.Textile.and.Leather & 0.41  & 1.39  & 0.12  & 2.69  & 40.17 & 1.32  & 1.11  & 1.15  & 9.51 \\
    Turkey.Transport.Equipment & 0.03  & 0.09  & 0.03  & 0.81  & 0.91  & 3.16  & 0.12  & 0.07  & 0.65 \\
    Germany.Agriculture & 0.93  & 2.25  & 0.16  & 2.31  & 2.06  & 0.51  & 29.88 & 5.25  & 9.60 \\
    Germany.Textile.and.Leather & 0.65  & 0.73  & 0.08  & 1.54  & 2.55  & 0.63  & 1.46  & 18.96 & 8.16 \\
    Germany.Transport.Equipment & 0.67  & 0.65  & 0.26  & 1.29  & 1.49  & 0.57  & 1.73  & 1.51  & 34.74 \\
    \hline
    \end{tabular}

\medskip

  \caption{Non-decomposed Values}
  \label{tab:noleon}
  \begin{tabular}{lccccccccc}
    \hline
         & Argentina. & Argentina. & Argentina. & Turkey. & Turkey. & Turkey. & Germany. & Germany. & Germany.\\
          & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport.\\
          & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
    \hline
    Argentina.Agriculture & 6.88  & 2.49  & 0.25  & 1.30  & 2.04  & 0.08  & 0.77  & 0.68  & 1.76 \\
    Argentina.Textile.and.Leather & 1.03  & 3.91  & 0.44  & 0.04  & 1.52  & 0.31  & 0.30  & 0.95  & 4.13 \\
    Argentina.Transport.Equipment & 0.38  & 0.24  & 0.55  & 0.00  & 0.05  & 0.06  & 0.00  & 0.10  & 0.18 \\
    Turkey.Agriculture & 0.47  & 0.93  & 0.03  & 7.33  & 6.27  & 1.20  & 2.23  & 0.75  & 3.19 \\
    Turkey.Textile.and.Leather & 0.13  & 1.37  & 0.01  & 2.48  & 13.35 & 1.24  & 0.52  & 0.61  & 9.19 \\
    Turkey.Transport.Equipment & 0.00  & 0.05  & 0.04  & 1.67  & 1.52  & 1.75  & 0.05  & 0.00  & 0.65 \\
    Germany.Agriculture & 0.51  & 2.05  & 0.04  & 1.67  & 0.57  & 0.12  & 7.18  & 4.73  & 6.43 \\
    Germany.Textile.and.Leather & 0.56  & 0.54  & 0.00  & 1.30  & 2.28  & 0.51  & 1.26  & 7.06  & 8.65 \\
    Germany.Transport.Equipment & 0.90  & 0.68  & 0.41  & 1.67  & 1.47  & 0.77  & 2.80  & 1.96  & 18.42 \\
    \hline
    \end{tabular}

@@

\begin{table}[hb!]
\scriptsize
\centering
\caption{Input Data}
\label{tab:leather}
\begin{tabular}{llrrrrrrrrrrrrrr}
  \hline
%&  & Argentina & Argentina & Argentina & Turkey & Turkey & Turkey & Germany & Germany & Germany & Argentina & Turkey & Germany &  \\
%        countries& industries & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & final & final & final & output\\
%         & & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
         & & \multicolumn{3}{c}{Argentina} & \multicolumn{3}{c}{Turkey} & \multicolumn{3}{c}{Germany} & \multicolumn{3}{c}{Final Demand} & Output \\
\hline
Country & Industry & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{Argentina} & \rotnt{Turkey} & \rotnt{Germany} \\
\hline
Argentina & Agriculture & 16.1 & 5.1 & 1.8 & 3.2 & 4.3 & 0.4 & 3.1 & 2.8 & 4.9 & 21.5 & 6.1 & 8.4 & 77.7 \\ 
Argentina & Textile.and.Leather & 2.4 & 8.0 & 3.2 & 0.1 & 3.2 & 1.6 & 1.2 & 3.9 & 11.5 & 16.2 & 1.9 & 5.1 & 58.3 \\ 
Argentina & Transport.Equipment & 0.9 & 0.5 & 4.0 & 0.0 & 0.1 & 0.3 & 0.0 & 0.4 & 0.5 & 11 & 0.5 & 0.8 & 19.0 \\ 
Turkey & Agriculture & 1.1 & 1.9 & 0.2 & 18.0 & 13.2 & 6.1 & 9.0 & 3.1 & 8.9 & 7.5 & 29.5 & 14.2 & 112.7 \\ 
Turkey & Textile.and.Leather & 0.3 & 2.8 & 0.1 & 6.1 & 28.1 & 6.3 & 2.1 & 2.5 & 25.6 & 8.9 & 24.9 & 16.9 & 124.6 \\ 
Turkey & Transport.Equipment & 0.0 & 0.1 & 0.3 & 4.1 & 3.2 & 8.9 & 0.2 & 0.0 & 1.8 & 1.2 & 18.5 & 4.9 & 43.2 \\ 
Germany & Agriculture & 1.2 & 4.2 & 0.3 & 4.1 & 1.2 & 0.6 & 29.0 & 19.5 & 17.9 & 9.2 & 17.9 & 51.2 & 156.3 \\ 
Germany & Textile.and.Leather & 1.3 & 1.1 & 0.0 & 3.2 & 4.8 & 2.6 & 5.1 & 29.1 & 24.1 & 7.9 & 10.1 & 38.5 & 127.8 \\ 
Germany & Transport.Equipment & 2.1 & 1.4 & 3.0 & 4.1 & 3.1 & 3.9 & 11.3 & 8.1 & 51.3 & 25.1 & 35.2 & 68.4 & 217.0 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

>>>>

\usepackage[latin1]{inputenc}
\usepackage{rotating}
\usepackage{adjustbox}
\usepackage{mathtools}
\usepackage{threeparttable}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{changepage}
\usepackage{lscape}
\usepackage{pbox}
\usepackage{array}
\usepackage[natbib, authordate, backend=biber]{biblatex-chicago}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

@@

\vspace{\stretch{1}}
\abstract{Global Value Chains have become a central unit of analysis in research on international trade. However, 
the complex matrix transformations at the basis of most Value Chain indicators still constitute a significant entry barrier to
the field. The R package \textit{decompr} solves this problem by implementing algorithms for the analysis of Global Value Chains,
which calculate standard indicators in an automated fashion. Two methods for gross export flow decomposition using 
Inter-Country Input-Output tables are provided. The first method is the \textit{Wang-Wei-Zhu} algorithm which splits 
bilateral gross exports into 16 value added components. These components can broadly be divided into domestic and 
foreign value added in exports. The second method concerns a decomposition based on the classical \citet{wale36} insight.
It derives the value added origins of an industry's exports by source country and source industry, using easily available
gross trade data. This article summarises the methodology of the algorithms, describes the format of the input and output data, 
and exemplifies the usefulness of the two methods on the basis of a simple example data set.}
\pagebreak

@@

\begin{enumerate}
 \item domestic value added in exports
 \item foreign value added in exports
 \item pure double counted terms
\end{enumerate}

@@

  \caption{Non-decomposed Values}
  \label{tab:noleon}
  \begin{tabular}{lrrrrrrrrr}
    \hline
         & Argentina. & Argentina. & Argentina. & Turkey. & Turkey. & Turkey. & Germany. & Germany. & Germany.\\
          & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport.\\
          & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
    \hline
    Argentina.Agriculture & 6.88  & 2.49  & 0.25  & 1.30  & 2.04  & 0.08  & 0.77  & 0.68  & 1.76 \\
    Argentina.Textile.and.Leather & 1.03  & 3.91  & 0.44  & 0.04  & 1.52  & 0.31  & 0.30  & 0.95  & 4.13 \\
    Argentina.Transport.Equipment & 0.38  & 0.24  & 0.55  & 0.00  & 0.05  & 0.06  & 0.00  & 0.10  & 0.18 \\
    Turkey.Agriculture & 0.47  & 0.93  & 0.03  & 7.33  & 6.27  & 1.20  & 2.23  & 0.75  & 3.19 \\
    Turkey.Textile.and.Leather & 0.13  & 1.37  & 0.01  & 2.48  & 13.35 & 1.24  & 0.52  & 0.61  & 9.19 \\
    Turkey.Transport.Equipment & 0.00  & 0.05  & 0.04  & 1.67  & 1.52  & 1.75  & 0.05  & 0.00  & 0.65 \\
    Germany.Agriculture & 0.51  & 2.05  & 0.04  & 1.67  & 0.57  & 0.12  & 7.18  & 4.73  & 6.43 \\
    Germany.Textile.and.Leather & 0.56  & 0.54  & 0.00  & 1.30  & 2.28  & 0.51  & 1.26  & 7.06  & 8.65 \\
    Germany.Transport.Equipment & 0.90  & 0.68  & 0.41  & 1.67  & 1.47  & 0.77  & 2.80  & 1.96  & 18.42 \\
    \hline
    \end{tabular}

\bigskip \bigskip

  \caption{Leontief Decomposition}
  \label{tab:leon}
  \begin{tabular}{lrrrrrrrrr}
    \hline
          & Argentina. & Argentina. & Argentina. & Turkey. & Turkey. & Turkey. & Germany. & Germany. & Germany.\\
          & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport.\\
          & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
    \hline
    Argentina.Agriculture & 28.52 & 2.79  & 0.36  & 1.81  & 3.12  & 0.36  & 1.24  & 1.30  & 4.12 \\
    Argentina.Textile.and.Leather & 1.06  & 19.12 & 0.42  & 0.48  & 1.83  & 0.43  & 0.59  & 1.15  & 4.75 \\
    Argentina.Transport.Equipment & 0.21  & 0.14  & 1.06  & 0.03  & 0.08  & 0.04  & 0.02  & 0.07  & 0.19 \\
    Turkey.Agriculture & 0.72  & 1.34  & 0.12  & 34.93 & 7.00  & 1.48  & 2.55  & 1.52  & 6.18 \\
    Turkey.Textile.and.Leather & 0.41  & 1.39  & 0.12  & 2.69  & 40.17 & 1.32  & 1.11  & 1.15  & 9.51 \\
    Turkey.Transport.Equipment & 0.03  & 0.09  & 0.03  & 0.81  & 0.91  & 3.16  & 0.12  & 0.07  & 0.65 \\
    Germany.Agriculture & 0.93  & 2.25  & 0.16  & 2.31  & 2.06  & 0.51  & 29.88 & 5.25  & 9.60 \\
    Germany.Textile.and.Leather & 0.65  & 0.73  & 0.08  & 1.54  & 2.55  & 0.63  & 1.46  & 18.96 & 8.16 \\
    Germany.Transport.Equipment & 0.67  & 0.65  & 0.26  & 1.29  & 1.49  & 0.57  & 1.73  & 1.51  & 34.74 \\
    \hline
    \end{tabular}

@@

\begin{table}[hb!]
\scriptsize
\centering
\caption{Input Data}
\label{tab:leather}
\begin{tabular}{llrrrrrrrrrrrrrr}
  \hline
         & & \multicolumn{3}{c}{Argentina} & \multicolumn{3}{c}{Turkey} & \multicolumn{3}{c}{Germany} & \multicolumn{3}{c}{Final Demand} & Output \\
\hline
Country & Industry & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{Argentina} & \rotnt{Turkey} & \rotnt{Germany} \\
\hline
Argentina & Agriculture & 16.1 & 5.1 & 1.8 & 3.2 & 4.3 & 0.4 & 3.1 & 2.8 & 4.9 & 21.5 & 6.1 & 8.4 & 77.7 \\ 
Argentina & Textile.and.Leather & 2.4 & 8.0 & 3.2 & 0.1 & 3.2 & 1.6 & 1.2 & 3.9 & 11.5 & 16.2 & 1.9 & 5.1 & 58.3 \\ 
Argentina & Transport.Equipment & 0.9 & 0.5 & 4.0 & 0.0 & 0.1 & 0.3 & 0.0 & 0.4 & 0.5 & 11 & 0.5 & 0.8 & 19.0 \\ 
Turkey & Agriculture & 1.1 & 1.9 & 0.2 & 18.0 & 13.2 & 6.1 & 9.0 & 3.1 & 8.9 & 7.5 & 29.5 & 14.2 & 112.7 \\ 
Turkey & Textile.and.Leather & 0.3 & 2.8 & 0.1 & 6.1 & 28.1 & 6.3 & 2.1 & 2.5 & 25.6 & 8.9 & 24.9 & 16.9 & 124.6 \\ 
Turkey & Transport.Equipment & 0.0 & 0.1 & 0.3 & 4.1 & 3.2 & 8.9 & 0.2 & 0.0 & 1.8 & 1.2 & 18.5 & 4.9 & 43.2 \\ 
Germany & Agriculture & 1.2 & 4.2 & 0.3 & 4.1 & 1.2 & 0.6 & 29.0 & 19.5 & 17.9 & 9.2 & 17.9 & 51.2 & 156.3 \\ 
Germany & Textile.and.Leather & 1.3 & 1.1 & 0.0 & 3.2 & 4.8 & 2.6 & 5.1 & 29.1 & 24.1 & 7.9 & 10.1 & 38.5 & 127.8 \\ 
Germany & Transport.Equipment & 2.1 & 1.4 & 3.0 & 4.1 & 3.1 & 3.9 & 11.3 & 8.1 & 51.3 & 25.1 & 35.2 & 68.4 & 217.0 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}
